\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage{times}
% Language setting
% Replace `english' with e.g. `spanish' to change the document language
\usepackage[english]{babel}
\usepackage{csquotes}
% Set page size and margins
% Replace `letterpaper' with `a4paper' for UK/EU standard size
\usepackage[a4paper,top=3cm,bottom=3cm,left=2cm,right=2cm]{geometry}
% \usepackage[left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm]{geometry}

\renewcommand{\baselinestretch}{1.15} 

% utility packages
\usepackage{graphicx} %allows for use of graphics
\usepackage{float} %float options for figures as [H]
\usepackage{subfiles} %allows for use of subfiles
\usepackage{tabularx} %tables that fill page
\renewcommand{\arraystretch}{1.4} % Makes rows taller
\usepackage{booktabs} %gives rule lines for tables
\usepackage{comment} %allows for commenting larger sections
\usepackage[colorlinks=false,hidelinks]{hyperref} %allows for hyperreferencing with no colored links and red boxes


% Useful packages
\usepackage{amsmath} %gives aligned environment for equations
\usepackage{amssymb} %usefull for math equations
\usepackage{siunitx} %SI units
\usepackage[style=ieee]{biblatex}
\usepackage{minted}
\usepackage{cleveref}
\usepackage{subcaption}
\usepackage{adjustbox}

\addbibresource{references.bib}

\setlength{\textfloatsep}{1pt}      % Space between text and floats
\setlength{\abovecaptionskip}{1pt}  % Space above captions
\setlength{\belowcaptionskip}{1pt}  % Space below captions
\setcounter{tocdepth}{2}
\begin{document}
\subfile{sections/frontpage.tex}

\tableofcontents
\thispagestyle{empty}


\newpage
\begin{abstract}
%The abstract should provide a comprehensive overview of your task, detailing the problem you are addressing, the algorithm you have selected/developed/applied, the dataset you used for evaluation, and the results you obtained. Please ensure the structure reflects a typical computer vision paper, focusing on clarity and conciseness.
Automated detection of epileptic seizures from Electroencephalography (EEG) data is critical for improving clinical workflows, patient care, and targeted neuromodulation therapies. Traditional visual inspection of massive EEG volumes by neurologists is slow, labor-intensive, and prone to human error. To address this, a hybrid deep learning framework is investigated, combining a Convolutional Neural Network (CNN) and a Long Short-Term Memory (LSTM) network to automatically extract local structural patterns and track temporal dependencies in sequential time-series data.

The proposed CNN-LSTM architecture is rigorously evaluated on the Bonn University EEG dataset for binary classification between healthy states and active seizures. To assess robustness on more complex temporal structures, the model is further benchmarked against a secondary hand-gesture dataset. Minimal preprocessing, featuring bandpass filtering and z-score normalization, is applied to preserve anomalous neural spikes. For the EEG task, data augmentation is achieved via 1-second segmenting with a 75\% overlap, utilizing stratified splits and weighted cross-entropy loss to combat class imbalances. Hyperparameters are optimized using a comprehensive 1152-configuration grid search followed by 5-fold cross-validation.

Experimental results demonstrate that the optimal CNN-LSTM model achieves a high classification reliability on the EEG dataset, yielding an average F1-score of 0.9895 and an accuracy of 99.30\%, with an exceptionally low error rate (0.26\% false negatives and 0.43\% false positives). While a baseline logistic regression model achieves comparable performance on the relatively simple EEG dataset (97\% accuracy), the CNN-LSTM significantly outperforms it on the complex gesture dataset, achieving an F1-score of 0.9562 and an accuracy of 95.70\% compared to the baseline's 80\% accuracy. These findings demonstrate the superior capability of the CNN-LSTM architecture in modeling intricate, long-running time-domain signals.

% \textit{Please note that the title page, abstract, table of contents, and pages containing references are not included in the final report length. Ensure that the main body of the report does not exceed 7-8 pages.}
\end{abstract}

\newpage

\subfile{sections/introduction.tex}
\setcounter{page}{1}
\subfile{sections/relatedworks.tex}
\subfile{sections/methodology.tex}
\subfile{sections/results.tex}
\subfile{sections/discussion.tex}
\subfile{sections/conclusion.tex}


% References
\newpage
%\bibliographystyle{apalike}  % Choose from: plain, apalike, ieeetr, etc.
%\printbibliography
\section{References}
\printbibliography[
heading=none
]
\newpage
\section{Acknowledgments}
Generative AI has been used in this report for proofreading, clarification and drafting of certain paragraphs.
\appendix
\section{Appendix}
\subsection{Source code link}
The source code of the project can be found on Github:
\url{https://github.com/Jack-The-Dane/KIV}
\subsection{5 best grid search models}
\label{app:gridsearch}
\begin{table}[h]
    \centering
    \begin{tabular}{c|c|c|c|c|c}
        Parameter    & Model 1 & Model 2 & Model 3 & Model 4 & Model 5 \\
        kernel\_size1 & 13     & 5       & 11      & 11      & 9       \\
        kernel\_size2 & 5      & 9       & 7       & 7       & 5       \\
        cnn\_internal & 32     & 64      & 128     & 64      & 64      \\
        cnn\_out      & 128    & 64      & 256     & 128     & 128     \\
        hidden\_size  & 128    & 64      & 128     & 256     & 64      \\
        num\_layers   & 2      & 2       & 3       & 1       & 2       \\
        dropout       & 0.5    & 0.5     & 0.5     & 0.5     & 0.2     \\
        learning\_rate& 0.001  & 0.001   & 0.001   & 0.001   & 0.001   \\
        weight\_decay & 0.0001 & 0.0001  & 0.0001  & 0.0001  & 0.0001  \\
        F1-score      & 0.9913 & 0.9912  & 0.9912  & 0.9891  & 0.9891 
    \end{tabular}
    \caption{Table showing the 5 best models, determined by F1-score, found by the grid search algorithm. All models were validated using hold-out validation with 10\% of data being used for the final evaluation of each model, 18\% being used for validation during training, and 72\% being used for training.}
    \label{tab:app_gridsearch}
\end{table}

\end{document}