\documentclass[a4paper,12pt]{article}

% Packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage[left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm]{geometry}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{caption}
\usepackage{enumitem}
\usepackage{natbib}

% Header and footer setup
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{T550021101-1-F25 Kunstig intelligens værktøjer, (F25)}
\fancyhead[R]{MSc Engineering - Drone Technology and Autonomous Systems}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

% Section formatting
\titleformat{\section}
  {\normalfont\large\bfseries}
  {\thesection}{1em}{}

% Title page setup
\title{
\vspace{-1.5cm}
\begin{center}
\large{\textbf{The Faculty of Engineering}}\\
\large{\textbf{The Maersk Mc-Kinney Moller Institute}}\\
\vspace{1cm}
\Huge{\textbf{Project Report}}\\
\vspace{2cm}
\end{center}
\vspace{-1cm}
}

\author{
\begin{tabular}{ll}
\textbf{Student Name:} & \\
\textbf{Student ID Number:} & \\
\textbf{Class and Year:} & Master of Science in Engineering Drone Technology and Autonomous Systems \\
& 2024--2026 \\
\textbf{Subject Code and Name:} & T550021101-1-F25 Kunstig intelligens værktøjer, (F25) \\
\textbf{Lecturer Name(s):} & Smith Khare and Vinay Chakravarthi Gogineni \\
\textbf{Title:} & Your project title \\
\textbf{Other Group Members:} & Leave this blank if you work alone \\
\textbf{Submission Date:} & 28-05-2025 \\
\end{tabular}
}

\date{}

\begin{document}

\maketitle

\vspace{1cm}
\noindent\fbox{
\parbox{\textwidth}{
\textbf{Academic Integrity and Plagiarism}\\
Plagiarism is the act of copying, including or directly quoting from, the work of another without adequate acknowledgment. All work submitted by students for assessment purposes is accepted on the understanding that it is their own work and written in their own words except where explicitly referenced using the correct format. For example, you must NOT copy information, ideas, portions of text, data, figures, computer programs, etc. from anywhere without giving a reference to the source. Sources can include websites, other students' work, books, journal articles, reports, etc. Self-plagiarism or auto-plagiarism is where a student re-uses work previously submitted to another course within the SDU or other Universities.\\
\vspace{0.2cm}
You must ensure that you have read the SDU regulations relating to plagiarism.\\
\vspace{0.2cm}
\textbf{I have read and understood the SDU code of practice on plagiarism and confirm that the content of this document is my own work and has not been plagiarized.}\\
\vspace{0.5cm}
Student's signature: \rule{5cm}{0.4pt}
}}

\newpage

\begin{abstract}
The abstract should provide a comprehensive overview of your task, detailing the problem you are addressing, the algorithm you have selected/developed/applied, the dataset you used for evaluation, and the results you obtained. Please ensure the structure reflects a typical computer vision paper, focusing on clarity and conciseness.

Please note that the title page, abstract, table of contents, and pages containing references are not included in the final report length. Ensure that the main body of the report does not exceed 7-8 pages.
\end{abstract}

\newpage
\tableofcontents
\newpage











\end{document}