\section{Introduction}
Epilepsy is a common neurological disorder characterized by recurrent seizures. Traditionally, neurologists identify these seizures by visually inspecting massive volumes of Electroencephalography (EEG) data, a process that is slow, labor-intensive, and prone to human error.

Automated seizure detection using EEG data is critical for:
\begin{itemize}
    \item Clinical Support: Assisting doctors by continuously monitoring patients and alerting hospital staff.
    \item Patient Care: Powering wearable devices that provide real-time warnings to reduce injury risks.
    \item Targeted Therapy: Enabling closed-loop neurostimulation systems that automatically trigger treatment upon detecting abnormal brain activity.
\end{itemize}

Seizure detection refers to the task of identifying patterns in EEG signals that indicate the presence of an epileptic seizure.
Because machine and deep learning excel at processing complex brain patterns without manual feature engineering, this project investigates a hybrid CNN-LSTM architecture. By combining the feature extraction power of Convolutional Neural Networks (CNNs) with the temporal tracking strengths of Long Short-Term Memory (LSTM) networks, this approach aims to accurately differentiate healthy brain signals from active epileptic seizures.

% This section should clearly describe your selected task. For example, if your task is image classification, begin by explaining what image classification is, why is its significance, and where it is commonly applied in real-world scenarios.

% About $\frac{1}{2}$ page.
